Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
+ CEGIS figure with precision/sampling incrementation

\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}

@@

We investigate two different approaches of integrating solution generalisation 
into CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
enables abstraction refinement inside the CEGIS loop. 
\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
increase of precision and sampling rate.
\end{itemize}

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with Abstraction Refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with Precision and Sampling Rate Incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

>>>>

\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}

@@

We investigate two different approaches of integrating solution generalisation 
into CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
enables abstraction refinement inside the CEGIS loop. 
\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
increase of precision and sampling rate.
\end{itemize}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General Architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

The design of our synthesizer 
%is given in Figure~\ref{fig:CEGIS} and 
consists of two phases, an inductive synthesis phase and a validation phase,
%{\sc Synthesize} and {\sc Verify}, 
which interact via a finite set of test vectors {\sc inputs} that is updated incrementally. 
Given the aforementioned specification $\sigma$, the inductive synthesis
procedure
tries to find an existential witness $\vec{P}$ satisfying the specification
$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
all $\vec{x} \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$\vec{P}$, this witness
is a candidate solution to the full synthesis formula.  We pass this
candidate solution to the validation phase, which checks whether it is a full
solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
%
%determines whether
%it does satisfy the specification on all inputs by checking
%satisfiability of the following verification formula:
%
%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
%If this formula is unsatisfiable, 
%% the candidate solution is in fact a 
%% full solution.
%
If this is the case, then the algorithm terminates.  Otherwise, additional
information is provided to the inductive synthesis phase in the form of a new
counterexample that is added to the {\sc inputs} set and the loop iterates
again.
%% the witness $\vec{x}$ denote an input on which the
%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
%% added to the {\sc inputs} set, and the loop iterates again.

It is
worth noting that each iteration of the loop adds a new input to the
finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
the full set of inputs $\mathcal{D}$
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
specialise the general CEGIS approach in order to perform solution generalisation.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with Abstraction Refinement}
\label{sec:CEGIS-abstraction-refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with Precision and Sampling Rate Incrementation}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

\begin{figure}[htb]
{\scriptsize
\centering
%\resizebox{.8\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Sampling}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Complete}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Sampling\\Verifier};
   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Completeness\\Verifier};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
   ([xshift=10.5cm]aux2) edge node[align=center] {Increase $k$} (aux1);

 \end{tikzpicture}
}}
\caption{The CEGIS loop with precision and sampling rate incrementation}
\label{fig:CEGIS}
\end{figure}
